---
title: "Table 10"
output: html_notebook
---
#I have a few ideas down below but I believe our best bet is to split it into two separate tables which is the last two chunks of code at the bottom

#Table 10. Imprisonment rates of U.S. residents, based on sentenced prisoners under the jurisdictions of state and federal correctional authorities, by demographic characteristics, December 31, 2019

## TABLE 10
##Note: Jurisdiction refers to the legal authority of state or federal correctional officials over a prisoner, regardless of where the prisoner is held. Rates and counts are based on sentenced prisoners under the jurisdiction of state or federal correctional officials. Imprisonment rate is the number of sentenced prisoners under state or federal jurisdiction per 100,000 U.S. residents, or per 100,000 U.S. residents in a given category. Resident population estimates are from the U.S. Census Bureau for January 1, 2020. Totals include imputed counts for Oregon, which did not submit 2019 National Prisoner Statistics data. See Methodology.

# number of new arrests/imprisonments were diagnosed for every 100,000 people.
```{r}
library(tidyverse)
```

```{r}
p19t10 <- read_csv("table10.csv")

p19t10
```
```{r}
set1 <- p19t10 %>%
  select(-c("X2","X4", "X10"))
set1
```
```{r}
#p19<-
  #set1 %>% 
  #mutate(mycol = coalesce(X1)) %>%
  #select(mycol)

#p19
```


```{r}
names(set1) <- as.matrix(set1[1, ])
set1 <- set1[-1, ]
set1[] <- lapply(set1, function(x) type.convert(as.character(x)))
View(set1)

```

```{r}
colnames(set1)[3] <- 'Male'
colnames(set1)[8] <- 'Female'

set1


```
```{r}
set1<-set1[-c(1,13), ]
set1
```


```{r}
#set11 <- 
  #set1 %>%
  #pivot_wider(names_from = Age, values_from = c(Male, Female))
#set11
```

```{r}
#set12 <- 
  #set1 %>%
  #pivot_wider(names_from = Age, values_from = c("White/a", "Black/a", "Hispanic", "Other/a,b"))
#set12
```

```{r}
#set13 <- 
  #set1 %>%
  #pivot_wider(names_from = Age, values_from = c("Total"))
#set13
```

```{r}
idea_table1 <-
  set1[ ,c(1,3:7)]
View(idea_table1)
#>>>>>>> 3c2adc2f826f13221a07b2d170bf95cf5de659fa
```

```{r}
idea_table1 <- map_df(idea_table1, ~gsub(",","", .x))
idea_table1_clean <- as.data.frame(sapply(idea_table1, as.numeric ))
ageRange<- c('18-19', '20-24', '25-29','30-24','35-39','40-44','45-49','50-54','55-59','60-64','65 or older')
idea_table1_clean$Age <- ageRange
```


```{r}
#<<<<<<< HEAD
idea1 <- 
  idea_table1_clean %>% #select(`White/a`, `Black/a`, Hispanic, `Other/a,b`) %>%
  pivot_longer(., cols = c(`White/a`, `Black/a`, Hispanic, `Other/a,b`), names_to = "Race", values_to = "Count")
idea1
```

```{r}
#esquisser(idea1)
#library(ggplot2)
```

```{r}

ggplot(idea1) +
 aes(x = Age, fill = Race, colour = Race, weight = Count) +
 geom_bar() +
 scale_fill_hue() +
 scale_color_hue() +
 labs(title = "Male Sentences Prisoners 2019 by Age and Race") + #change the title to something more concrete 
 theme_bw() +
 facet_grid(vars(Race), vars())
#=======
```





```{r}
idea_table2 <-
  set1[ ,c(1,8:12)]
idea_table2
```

```{r}
idea_table2 <- map_df(idea_table2, ~gsub(",","", .x))
idea_table2_clean <- as.data.frame(sapply(idea_table2, as.numeric ))
ageRange<- c('18-19', '20-24', '25-29','30-24','35-39','40-44','45-49','50-54','55-59','60-64','65 or older')
idea_table2_clean$Age <- ageRange

idea_table2_clean
```



```{r}
idea2 <- 
  idea_table2_clean %>% #select(`White/a`, `Black/a`, Hispanic, `Other/a,b`) %>%
  pivot_longer(., cols = c(`White/a`, `Black/a`, Hispanic, `Other/a,b`), names_to = "Race", values_to = "Count")
```


```{r}
ggplot(idea2) +
 aes(x = Age, fill = Race, colour = Race, weight = Count) +
 geom_bar() +
 scale_fill_hue() +
 scale_color_hue() +
 labs(title = "Female Sentenced Prisoners by Age and Race in 2019") + #change the title to something more concrete 
 theme_bw() +
 facet_grid(vars(Race), vars())
```


=======
>>>>>>> 3c2adc2f826f13221a07b2d170bf95cf5de659fa

#lesson 4 pairs??? is this unsupervised 

```{r}
#data.frame(lapply(idea_table1_clean,as.numeric))
i <-
  idea_table1_clean %>%
  select(-Age)
data.frame(lapply(i,as.numeric))

```

```{r}
pairs(i)
#pairs(idea_table1)
#pairs(idea2)
```
```{r}
eu_dist <- get_dist(idea_table1, method = 'euclidean')
image(as.matrix(eu_dist), main = "Euclidean distance")
```

```{r}
hc_complete <- hclust(eu_dist, method='complete') # for complete linkage...merge distance of cluster, the fartherest points
hc_complete
hc_complete$merge %>% head()
hc_complete$height %>% head()
plot(hc_complete) 

```
#use this type...look at lesson 5 for info on all this stuff
```{r}
fviz_dend(hc_complete)

```
```{r}
fviz_dend(hc_complete, k = 2, k_colors = "jco", as.ggplot = TRUE, show_labels = FALSE, main='Euclidean-Complete')

```
#ERROR!!!!!!

```{r}
cluster_h <- cutree(hc_complete, k = 2) #identifying 2 groups
cluster_h
pairs(idea_table1, col = cluster_h) # our result
#pairs(iris2, col = species)
```

```{r}
fviz_dend(hc_complete, h = 2, k_colors = "jco", as.ggplot = TRUE, show_labels = FALSE, main='Euclidean-Complete')
cluster_h <- cutree(hc_complete, h = 5) #identifying 3 groups by cutting at height h=5...cut with the longest 3 branches
cluster_h
```
```{r}
hc_diana <- diana(eu_dist)
str(hc_diana)
```

```{r}
fviz_dend(hc_diana, as.ggplot = TRUE, show_labels = FALSE, main='Euclidean-Complete')#plot the dendrogram

```
```{r}
cluster_diana <- cutree(hc_diana, k=3) # cut by k (with height? Error)
cluster_diana

#pairs(iris2, col=cluster_diana)
```


# kmeans
```{r}
res <- idea1 %>% kmeans(3)
str(res)
```













```{r}
res <- idea_table1 %>% prcomp(scale = TRUE) #this function does what we need...no code necessary....takes every column and scales it, we transform the mean of each single column to zero 
str(res)
loadings <- res$Male 

```

<<<<<<< HEAD

#time to use unsupervised learning

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
```


```{r}
set.seed(123)
fviz_nbclust(idea1, kmeans, method = "wss")
```
```{r}
fviz_nbclust(idea1, hcut, hc_method = "complete", hc_metric = "euclidean", method = "wss") +
  labs(title = "Optimal Number of Clusters for Male")
fviz_nbclust(idea2, hcut, hc_method = "complete", hc_metric = "euclidean", method = "wss") +
  labs(title = "Optimal Number of Clusters for Female" )

```
```{r}
res <- idea1 %>% prcomp(scale = TRUE)
fviz_screeplot(idea1, main='Scree Plot for the Decathlon2 Data')

fviz_nbclust(idea1, kmeans, method = "silhouette")+
  labs(subtitle = "Silhouette method")
```

#random thing from HW3
```{r}
ageRange<- c('0', '1', '2','3','4','5','6','7','8','9','10')
age <- as.numeric(ageRange)
idea_table1_clean$Age <- age
#idea_table1_clean #%>%
#  as.numeric(Age)
idea_table1_clean
```

```{r}
#hi <- 
#  idea_table1_clean %>%
 # select(-Age)
  
scatter1 <- 
  idea_table1_clean %>% #call the dataset
  select(-Age)%>%
  scale() 
scatter1

age <- idea_table1_clean$Age

pairs(scatter1, col = age  , main = "Relationship") #factors columns to form matrix, colors from rape
cor(scatter1)


scatter2 <-
  idea_table1_clean %>%
  select(-`Other/a,b`) %>%
  scale()
scatter2

other <- idea_table1_clean$`Other/a,b`
pairs(scatter2, col = other, main = "relationship")
cor(scatter2)
```






## I am adding this comment in hopes that the token works hi!!
